% Template for ICASSP-2010 paper; to be used with:
%          mlspconf.sty  - ICASSP/ICIP LaTeX style file adapted for MLSP, and
%          IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------
\documentclass{article}
\usepackage{amsmath,graphicx,02456}
\usepackage{float}
\usepackage{appendix}

\toappear{02456 Deep Learning, DTU Compute, Fall 2021}

% Example definitions.
% --------------------
\def\x{{\mathbf x}}
\def\L{{\cal L}}

% Title.
% ------
\title{Insect Classification Using Long Short-Term Memory}
%
% Single address.
% ---------------
\name{Freja Thoresen (S213769), Pascal Dufour (S011602), Nikolaj Sheller (C971666)\thanks{Thanks to FaunaPhotonics A/S for insect data.}}

\address{DTU \\ Department of Applied Mathematics and Computer Science}

%\author{
%  Thoresen, Freja\\
%  \texttt{first1.last1@xxxxx.com}
%  \and
%  LastName2, FirstName2\\
%  \texttt{first2.last2@xxxxx.com}
%  \and
%    LastName2, FirstName2\\
%  \texttt{first2.last2@xxxxx.com}
%}


%
% For example:
% ------------
%\address{School\\
%	Department\\
%	Address}
%
% Two addresses (uncomment and modify for two-address case).
% ----------------------------------------------------------
%\twoauthors
%  {A. Author-one, B. Author-two\sthanks{Thanks to XYZ agency for funding.}}
%	{School A-B\\
%	Department A-B\\
%	Address A-B}
%  {C. Author-three, D. Author-four\sthanks{The fourth author performed the work
%	while at ...}}
%	{School C-D\\
%	Department C-D\\
%	Address C-D}
%
\begin{document}
%\ninept
%

\maketitle
%
\begin{abstract}
The FaunaPhotonics insect sensor, can detect insects by observing near-infrared back-scattered light. 
The aim of this project is to classify signals as insects or not insects.
\end{abstract}
%
\begin{keywords}
insects, detection, non-destructive, unsupervised, near-infrared
\end{keywords}
%
\section{Introduction}
\label{sec:intro}

Automated, non-destructive insect detection in fields can improve pest control and spare beneficial insects in crops\cite{Kirkeby2021}. The FaunaPhotonics insect sensor\cite{rydhmer2021automating}, the Volito, can detect insects by near-infrared (NIR) back-scatter. 
The data provided by a Volito can be classified as insects, or not insects. 

The challenge is to do so reliably and quickly.

The Volito emits NIR and detects back-scatter using a charge-coupled device (CCD) sensor. NIR back-scatters off an insect's carapace and wings as specular and diffuse reflections.
The reflections and wing-beat frequency (WBF) produce a signature of the insect, that a deep neural network can be trained to identify and classify.
The CCD is sampled at $\sim$20KHz and produces a waveform when an insect traverses the probe volume, that is very similar to an audio signal a given insect produces, when flying. 
For a farmer to map insect prevalence an a field, the sensor must to be mounted on a moving platform, e.g. a tractor or spraying boom. When the sensor is in motion, significant noise is introduced in the acquired signal, e.g. from equipment vibration, crops traversing the probe volume etc.
The classification of insects need to be real-time such that the spraying boom can spray detected insects, while holding off in areas without activity.
This requires that our classification network be very robust to e.g. noise, rapid changes in baseline and vibration, while classifying real-time.


\input{Sections/Datasets}
\input{Sections/Results}
\input{Sections/Conclusion}


% References should be produced using the bibtex program from suitable
% BiBTeX files (here: strings, refs, manuals). The IEEEbib.bst bibliography
% style file from IEEE produces unsorted bibliography list.
% -------------------------------------------------------------------------
\bibliographystyle{IEEEbib}
\bibliography{refs}

\end{document}
